Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-18 doc/JFLA2022/paper.tex
Why we cannot migrate to Dune just yet.

In practice, we still support building the whole project using \make via the \coqmakefile tool bundled with \coq, and we actually rely on this build system in our documentation generation pipeline. The main reason is that using \coqmakefile is currently more convenient than Dune for local IDE-based Coq code development, e.g., due to Dune placing generated files in a separate directory. We expect to migrate fully to Dune in the near future.

>>>>

However, Dune is still inconvenient for local IDE-based Coq code development and does not yet support building Coqdoc files.
%
Therefore, we still support building the whole project using \make via the \coqmakefile tool bundled with \coq, and we rely on this build system in our documentation generation pipeline.
%
We expect to migrate fully to Dune as soon as these limitations are lifted.
